Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-28 report/report.tex
Add figure with feature overlap cases

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_feature_overlap_cases}
    \caption{The 5 identified cases over feature overlap. Top left: A building lies in paralel with a road, and the distance between the two is smaller than the minimum width of the road. Top right: A road shares a node with a building. Middle: A road is intersecting with certain building features. Bottom left: Two roads have a minimum distance that is smaller than the sum of the minimum widths of both roads. Bottom right: Two roads share a node, and a subsequent node in one road lies within the minimum width of the other road.}
    \label{fig:space}
\end{figure}

All these cases will create issues when generating the 3D mesh representation of the city.
